*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-04 Code/Manuscript_O2.Rmd

Figures \@ref(fig:MED4OverlayPlots), \@ref(fig:SS120OverlayPlots) and
\@ref(fig:MIT9313OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P. marinus* MED4, SS120 and MIT9313, respectively. Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR versus imposed PAR for each *P. marinus* and each spectral waveband.

@@

```{r MED4OverlayPlots, fig.cap = MED4OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}

@@

```{r SS120OverlayPlots, fig.cap = SS120OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}

@@

```{r MIT9313OverlayPlots, fig.cap = MIT9313OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}

@@

```{r MaxGrowthTable, fig.height = 6, fig.width = 8, echo = FALSE }

@@

>>>>

Figures \@ref(fig:OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P. marinus* MED4, SS120 and MIT9313, respectively. Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR versus imposed PAR for each *P. marinus* and each spectral waveband.

@@

```{r OverlayPlots, fig.cap = OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}

OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 (A,B,C); SS120 (D,E,F); MIT9313 (G,H,I) grown under three emission wavebands.**",
                       "**(A,D,G)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
                       "**(B,E,H)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).", 
                       "**(C,F,I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",

knitr::include_graphics(file.path(FiguresIn, "OverlayPlots.png"))

```{r MED4OverlayPlots, fig.cap = MED4OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}

@@

```{r SS120OverlayPlots, fig.cap = SS120OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}

@@

```{r MIT9313OverlayPlots, fig.cap = MIT9313OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}

@@

```{r MaxGrowthTable, echo = FALSE }

@@

```{r ProchlorococcusEnzymeTable, echo = FALSE }

readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
  knitr::kable(.,
             caption = "Enzyme Commission numbers (EC) and corresponsing enzyme names.",
            col.names =  c("EC",
                          "Enzyme Name")
             )
